---
title: "regulaTEr"
output: github_document
---

<!-- badges: start -->
<!-- badges: end -->

**regulaTEr** implements the methods of Kwon and Sun (2025) to estimate treatment effects under bounds on their heterogeneity.

## Installation

You can install the development version of **regulaTEr** from [GitHub](https://github.com/) with:

```r
# install.packages("pak")
# install.packages("devtools")
devtools::install_github("lsun20/regulaTEr")
```

## Functions
- `regulaTE()`: Calculates the regulaTE estimate and comparison estimators (short, bias-corrected short, and long) for the treatment effects under a specified bound on treatment effect heterogeneity.
- `plot_regulaTE()`: Plots the estimates from `regulaTE()` varying the bound on treatment effect heterogeneity.

## Example

The following is a basic example illustrating how **regulaTEr** estimates ATE bounds under heterogeneity.

A small dataset is generated with four strata \(X \in \{1,2,3,4\}\). Each stratum has (i) a treatment probability, (ii) baseline outcomes \(Y_0\), and (iii) heterogeneous treatment effects \(\tau(X)\). From this, we simulate individual outcomes and run `regulaTE()`.


```{r example, echo = TRUE}
#library(regulaTEr)
devtools::load_all(".")

rawdata <- data.frame(
  X = c(1, 2, 3, 4),
  probTreat = c(0.1, 0.5, 0.5, 0.9),
  probX = c(0.25, 0.25, 0.25, 0.25),
  Y0mean = c(0, 0, 0, 0),
  tauX = c(0, 5, 5, 0)
)

sigma <- 5
set.seed(1)
sim_size <- 500
simdata <- rawdata[sample(seq_len(nrow(rawdata)), size = sim_size, replace = TRUE, prob = rawdata$probX), ]
simdata$x <- as.integer(runif(sim_size) < simdata$probTreat)

Xvalues <- unique(simdata$X)
for (i in seq_along(Xvalues)) {
  dummy <- as.integer(simdata$X == Xvalues[i])
  if (sum(dummy) > 0) {
    simdata[[paste0("Z", i)]] <- dummy
  }
}
Z_uc <- as.matrix(simdata[, grep("^Z", names(simdata))])
Z_uc <- Z_uc[, -ncol(Z_uc)]  # drop last column to avoid collinearity

simdata$Y1mean <- simdata$Y0mean + simdata$tauX
C0 <- sd(simdata$tauX)
simdata$Y1 <- rnorm(sim_size, mean = simdata$Y1mean, sd = sigma)
simdata$Y0 <- rnorm(sim_size, mean = simdata$Y0mean, sd = sigma)
simdata$Y <- simdata$x * simdata$Y1 + (1 - simdata$x) * simdata$Y0

result <- regulaTE(
  outcome = simdata$Y,
  treatment = simdata$x,
  covariates = Z_uc,
  confounders = NULL,
  parameter = "ATE",
  C = C0,
  se = "hom",
  cluster = NULL,
  sig_level = 0.05,
  df_corr = TRUE,
  digits = 4,
  trimmed_data = NULL
)
```


The output reports:

- The **regulaTE** estimate for the ATE under the specified heterogeneity bound \(C\),
- The **short** estimate (with and without bias corrections),
- The **long** estimates
- Standard errors, confidence intervals, and maximum bias given \(C\). 

In addition to reporting point estimates at a single value of \(C\), **regulaTE** can trace how the estimated treatment effects and its confidence set change as we vary the heterogeneity bound \(C\). Below we construct a grid of \(C\) values and plot the estimates using `plot_regulaTE()`.

```{r example-plot, echo = TRUE,fig.width = 12, fig.height = 8}
C_ran <- seq(0, 2 * C0, 0.1)

result <- regulaTE(
  outcome = simdata$Y,
  treatment = simdata$x,
  covariates = Z_uc,
  confounders = NULL,
  parameter = "ATE",
  C = C_ran,
  se = "hom",
  cluster = NULL,
  sig_level = 0.05,
  df_corr = TRUE,
  digits = 4,
  trimmed_data = NULL
)
plot_regulaTE(result$estimates, y_axis_title = "Outcome", title = NULL, show_long = FALSE)
```
